The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task

### 2017-02-03 docs/language_constraint.tex
Roy V3 (not final)

%\renewcommand{\ms}[1]{}
%\renewcommand{\roy}[1]{}
%\renewcommand{\nascomment}[1]{}
%\renewcommand{\yc}[1]{}
%\renewcommand{\royb}[1]{}
%\renewcommand{\royc}[1]{}

@@

\begin{document}
\maketitle
\begin{abstract}
%People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
% People's writing style depends not just on the authors' personal
% traits but also on the intent and the cognitive states of the
% authors. 
A writer's style depends not just on personal traits but also on her
intent and cognitive state.
%In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
In this paper, we show how writing tasks involving different cognitive processes can lead to measurable differences in writing style. % of the same authors.  
%As a case study, we experiment with a recently published machine reading task: 
We present a case study based on 
the  {\it story cloze task} \cite{Mostafazadeh:2016}, %.
%In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story on their own vs.~adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent or incoherent.\clinic{Many felt these 2 contraints looks like 3 constraints. clarify} 
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a simple linear classifier informed with stylistic features obtains 
state-of-the-art results on the story cloze challenge,
substantially higher than  deep learning models,
even without looking at the story context. 
%Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
Our results demonstrate that different task framings can dramatically affect the way people write.\clinic{Similarly to previous comment: which results does this comment address?} 
\resolved{They also provide important lessons for designing new NLP
tasks. \nascomment{drop this sentence if we only have a paragraph
  about this at the end, as we currently do}}

@@

\section{Introduction}
Writing style is 
%defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
%It is often affected by inter-writer 
It is influenced by both 
personal 
factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, 
%or mere 
and personality \cite{Stamatatos:2009}, 
%but also by other parameters 
as well as the cognitive states\clinic{Avoid using ``cognitive"?} of the authors such as 
%such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.
sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
In this paper, we study 
%to what extent is 
the extent to which 
writing style is affected by 
the nature of the writing task the writer was asked to perform, since
different tasks likely engage different cognitive processes \cite{Banerjee2014KeystrokePA}.
%\clinic{Add citation}
%that would involve different cognitive processes.

\begin{table}[!t]
%\small
\begin{tabular}{|p{1.6cm}|p{5.3cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\color{blue}{Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\color{forestgreen}{Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
{\color{red}{Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}
Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{Original}} story written by one author. 
The second and third row show revised stories with two contrastive endings:
 %of the same story: 
 a {\color{forestgreen}{Coherent}} ending and a {\color{red}{Incoherent}} one.\clinic{They said it would be great to have three endings to the same story. Unfortunately Nasrin et al.  didn't publish the original endings for the dev/test data. We could ask her, but not sure if this is worth it}
 \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
let's consider just color-coding these three terms.  It's less distracting.}}
}
%\end{center}
\end{table}

%As a testbed, we experiment with
As a case study, we present experiments   based on 
the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
In this task, crowdsourced authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
%Following, 
Then, 
%the stories were given to other authors, 
each original story was given to a different author, 
who was shown only the first four sentences as a story context, 
and asked to write contrastive story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
%The goal of the task is to determine which of the endings is the correct one.
Framed as a story cloze task, the goal of this dataset was to serve as
a commonsense challenge for NLP and AI research. 
\tabref{ROC-example} shows an example of an {\it original} story, a {\it coherent} story, and an {\it incoherent} story.

While originally designed to be 
%a machine reading task, 
a story understanding challenge, 
%the compilation of this task 
the annotation process  
%raises several research questions
triggers interesting questions 
%which seem to differ from the original intent of the designers.
that may go beyond the original intent of the designers.
First, do 
%authors use different
people maintain the same writing 
style when asked to write  
%a {\it right} ending, compared to a {\it wrong} ending?
both coherent and incoherent story endings? Second, do people  
%use different style when composing the final sentence as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it right}) ending?
maintain the same writing style\clinic{What is style? (Luke)} when writing the entire story on their own compared to 
writing only the final sentence for a given story context written by someone else?

%Our analysis indicates that the answer to both questions is positive. 
Our analysis indicates that different framings of similar writing tasks 
can lead to measurable differences in people's writing style.\clinic{This is the main message -- should come earlier}
%We experiment with a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
%First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between the {\it right} and {\it wrong} endings in 64.5\% of the cases. 
Using a simple classifier informed with stylistic features, we show that our classifier can distinguish the {\it right} and {\it wrong} endings with 64.5\% accuracy, even without looking at the story context, where chance performance is 50\%.
%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
%Second, when trained to distinguish between the {\it original} endings and the new ({\it right}) endings, the classifier obtains 68.5\% accuracy. 
Further, our classifier can also distinguish between the {\it original} endings and the new ({\it right}) endings with 68.5\% accuracy, again without looking at the story context. \clinic{Why do we care? (Luke)}

@@

In order to further estimate the quality of our results, we 
%turn back to the story cloze task.
also directly tackle the story cloze challenge. 
Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase 
%compared to the published state-of-the-art results 
over the previously reported state of the art 
\cite{Salle:2016}.\clinic{Too many numbers in these paragraphs}
%When analyzing the results of our classifier, we see that sentiment plays a significant role in its success, which suggests that constraining authors to ``wrong'' sentences results in negative text.
We analyze the results of our classifier, and show that when distinguishing between {\it right} and {\it wrong} endings,  \resolved{\nascomment{feels like a leap here, maybe
  change wording a bit -- will come back to this.  note after reading
  all the way to the end:  need to be careful about conclusions drawn
  from weights alone }} sentiment plays a significant role: authors writing the wrong endings often engage negative sentiment.\roy{Better wording? we keep it depending on whether we keep our methodology}\clinic{more details required?}

Finally, we show that the style differences captured by our model can be combined with 
%a state-of-the-art machine reading tool, for which this task was designed, in order to obtain increased performance on the story cloze task.  
neural language models to make a better use of the story context. 
%We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
%We add the resulting probabilities as features in our linear classifier, and get 
Our final model that combines context with stylistic features achieves
75.2\%---an additional 2.8\% gain, 15.3\% better than the best
published result.\resolved{\footnote{
%Recently, a shared task for the story cloze
%  task has been conducted (\url{https://competitions.codalab.org/competitions/15333}). At the time of submission, the leading results was 71.1\%,
%%, which is  closer to our results, although still inferior.
%%No details about the validity of this result or the methods used to generate it are available.
%but no details are available for their results. 
I commented out this footnote, because we mention this later.  We
should only mention it once and not in the intro.
}}
%For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.

@@

%Our results may have a wide impact on a range of fields. 
The contributions of our study are threefold. 
First, findings from our study can potentially shed light on 
%cognitive processes that take place in the brain during writing.
how different kinds of cognitive load influence the style of written language. 
%Second, our results might have a more practical value in an era when fake news are becoming prominent,
%as they suggest that these might have different style compared to real news.
Second, our results provide valuable insights for designing new NLP tasks,\clinic{unclear}
both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant. 
Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.

The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
We then present our model, experiments and results in Sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present a further analysis of our results  and a discussion, followed by related work and conclusions.\clinic{Omit this paragraph?}

\isection{Background: The Story Cloze Task}{ROC_Story}
To understand how different writing tasks affect writing style, 
we focus on the \textit{story cloze task} \cite{Mostafazadeh:2016}. 
While this task was developed to facilitate representation and learning of commonsense story understanding,
it introduces a few interesting properties\clinic{which properties?} which make it ideal for our study. 
We describe the task below.

@@

\paragraph{ROC Stories.}

@@

\paragraph{Story Cloze Task.}
After compiling the story corpus, the {\it story cloze task}---a task based on the corpus---was introduced.
A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
Both endings are required to complete the story using one of the characters in the story context. 
Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.

@@

Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it story cloze task}. 
The task is simple:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
%The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
The official training data contains only the original stories (without alternative endings), while development and test data consist only of the revised stories with alternative endings (for a different set of original stories that are included in the training set). 
The task was suggested as an extensive evaluation framework:
%as a machine reading task, 
as a commonsense story understanding task, 
as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.

\paragraph{A Hard Task.}\roy{Was ``State-of-the-art results". Luke mentioned that this puts the focus on our results rather than on the nature of the task, as we intended}
Interestingly, at the time of this submission, 10 months after the
task was first introduced, the published benchmark on this task is
still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
  task website (\url{https://competitions.codalab.org/competitions/15333}) does report higher results (71.1\%), which are still
  unpublished along with the underlying methodology.}
This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar or shorter period of time.
This suggests that this task is challenging and that high performance is hard to achieve.
 \resolved{\yc{SQuAD was officially published in Nov 2016. by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper. Given that, the statement of this paragraph seems a bit of overkill...?} \nascomment{it sounds like Yejin is saying that on squad, there was an even faster acceleration?  or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}

\paragraph{Different Writing Tasks in the Story Cloze Task.}
\citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
Furthermore, the authors implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
These results indicate that real understanding of text is required in order to solve the task.

Several key design decisions make this task an interesting testbed for our purpose.\clinic{Which purpose?}
First, the training set for the task (ROC Stories corpus) is not a
training sample in the usual sense,\footnote{I.e., the training
  instances are drawn from a population similar to the one that future
  testing instances will be drawn from.}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
 \resolved{\yc{As far as I understand, this was intentional --- they didn't want
  people to pick up on random superfluous cues that can inevidently
  get into the data creation process, exactly the kind that our work
  picks up. Given that, stating this can be viewed as
  misunderstanding, I'm afraid.} \nascomment{We should maybe say that
  they did this intentionally and concede that our approach goes
  against the intentions of their task design.  But a task that
  insists that systems avoid using features that might encode one kind
of information (like style) is absurd.  Alternately, we could reframe
this not as ``things weren't controlled for'' but instead stick to the
facts here and just describe what they did without judgment.}}

On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets. 
While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
and then asking her to generate a fifth {\it right} ending. 
This raises the question of whether these different writing setups impose different writing styles. 
% We show that this is indeed the case.

@@

\isection{Surface Analysis.}{Surface}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between different groups. 
First, {\it original} endings are on average longer (11 words per
sentence) than {\it right} endings (8.75 words), which are in turn
slightly longer than {\it wrong} ones (8.47 words). This is inline with findings by \citet{yanchevaautomatic,qin2004exploratory}, which found that sentence length was indicative of whether a text was deceptive. Furthermore, \citet{buller1996interpersonal} suggests lying increases one's cognitive load, which in turn could affect sentence length.
%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings,
which in turn prefer proper nouns, especially compared to {\it original} endings. 
\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
% The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.
Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones. \ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, is there anything there?}.
Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates''). This is in line with previous findings that dececptively written text expresses more negative emotion compared to truthful text \cite{Newman:2003}.
%\yc{Again, any cogsci literature on this?} \nascomment{feels
%  Pennebaker-ish, that might be a good place to look.}
Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.

@@

        \legend{NN, VBD, PRP, DT, NNP}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_pos_distribution}POS tags}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
%        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=0,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it original}, 3.4) ({\it right}, 3.9) ({\it wrong}, 4)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it original}, 2.8) ({\it right}, 2) ({\it wrong}, 1.5)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it original}, 1.1) ({\it right}, 1.4) ({\it wrong}, 1.6)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it original}, 0) ({\it right}, 0) ({\it wrong}, 0.7)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it original}, 0.1) ({\it right}, 0.2) ({\it wrong}, 0)};

>>>>

%\renewcommand{\ms}[1]{}
\renewcommand{\roy}[1]{}
%\renewcommand{\nascomment}[1]{}
%\renewcommand{\yc}[1]{}
%\renewcommand{\royb}[1]{}
%\renewcommand{\royc}[1]{}

@@

\begin{document}
\maketitle
\begin{abstract}
%People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
% People's writing style depends not just on the authors' personal
% traits but also on the intent and the cognitive states of the
% authors. 
A writer's style depends not just on personal traits but also on her
intent and mental state.
%In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
In this paper, we show how writing tasks involving different mental processes can lead to measurable differences in writing style. % of the same authors.  
%As a case study, we experiment with a recently published machine reading task: 
We present a case study based on 
the  {\it story cloze task} \cite{Mostafazadeh:2016}, %.
%In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
where annotators were assigned similar writing tasks with different constraints: 
(1) writing an entire story on their own (2) adding only a story ending for a given story context, and (3) writing an incoherent ending to a story.\resolved{\clinic{Many felt these 2 contraints looks like 3 constraints. clarify}}
%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
We show that a simple linear classifier informed with stylistic features is able to successfully distinguish between the three cases.
Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}
In addition, our style-based classifier obtains state-of-the-art results on the story cloze challange, substantially higher than  deep learning models,
even without looking at the story context. 
%Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors.

\resolved{They also provide important lessons for designing new NLP
tasks. \nascomment{drop this sentence if we only have a paragraph
  about this at the end, as we currently do}}

@@

\section{Introduction}
Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
It is influenced by both personal factors such as age \cite{Schler:2006} and gender \cite{Argamon:2003}, 
by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
as well as mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.

\begin{table}[!t]
%\small
\begin{tabular}{|p{1.6cm}|p{5.3cm}|} \hline
{\bf Type} & {\bf Example} \\ \hline
{\color{blue}{Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
{\color{forestgreen}{Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
{\color{red}{Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
\end{tabular}
\caption{\label{ROC-example}
Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{Original}} story written by one author. 
The second and third rows show revised stories with two contrastive endings:
 %of the same story: 
 a {\color{forestgreen}{Coherent}} ending and a {\color{red}{Incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story. Unfortunately Nasrin et al.  didn't publish the original endings for the dev/test data. We could ask her, but not sure if this is worth it}}
 \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
let's consider just color-coding these three terms.  It's less distracting.}}
}
%\end{center}
\end{table}

We show that different framings of similar writing tasks can lead to measurable differences in people's writing style.
We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
Our results hint that different writing tasks impose different cognitive constraints on the writer, which lead to the substantial style differences.

%As a testbed, we experiment with
As a case study, we present experiments   based on 
the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
%Following, 
Then, 
%the stories were given to other authors, 
each original story was given to a different author, 
who was shown only the first four sentences as a story context, 
and asked to write contrastive story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.

\com{While originally designed to be a story understanding challenge, the annotation process triggers interesting questions 
that may go beyond the original intent of the designers.
First, do people maintain the same writing 
style when asked to write both coherent and incoherent story endings? 
Second, do people maintain the same writing style when writing the entire story on their own compared to 
writing only the final sentence for a given story context written by someone else? }

\com{
%Our analysis indicates that the answer to both questions is positive. 
Our analysis indicates that different framings of similar writing tasks 
can lead to measurable differences in people's writing style.\clinic{This is the main message -- should come earlier}
%We experiment with a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
%First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between the {\it right} and {\it wrong} endings in 64.5\% of the cases. 
Using a simple classifier informed with stylistic features, we show that our classifier can distinguish the {\it right} and {\it wrong} endings with 64.5\% accuracy, even without looking at the story context, where chance performance is 50\%.
%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
%Second, when trained to distinguish between the {\it original} endings and the new ({\it right}) endings, the classifier obtains 68.5\% accuracy. 
Further, our classifier can also distinguish between the {\it original} endings and the new ({\it right}) endings with 68.5\% accuracy, again without looking at the story context. \clinic{Why do we care? (Luke)}
}

\com{We show that a linear classifier informed with stylistic features can distinguish between {\it original}, {\it right} and {\it wrong}  endings to a large degree, even without looking at the story context.
Our results allow us to make a few key observations.
First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
Second,  people change their writing style when writing the entire story on their own compared to 
writing only the final sentence for a given story context written by someone else.}

%Our binary classification results range between 64.5\%--75.6\%, where chance performance is 50\%.

@@

While originally designed to be a story understanding challenge, 
 the annotation process introduced three variants of the same writing task: {\it original}, {\it right} and {\it wrong} endings. 
We show that a linear classifier informed with stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5\%--75.6\% binary classification results).
Our results allow us to make a few key observations.
First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
Second,  people change their writing style when writing the entire story on their own compared to 
writing only the final sentence for a given story context written by someone else.

In order to further estimate the quality of our results, we also directly tackle the story cloze challenge. 
 Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase over the previously reported state of the art  \cite{Salle:2016}.
We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
Our final model that combines context with stylistic features achieves
75.2\%---an additional 2.8\% gain, 15.3\% better than the best
published result.

@@

%Our results may have a wide impact on a range of fields. 
The contributions of our study are twofold. 
First, findings from our study can potentially shed light on 
%cognitive processes that take place in the brain during writing.
how different kinds of cognitive load influence the style of written language. 
%Second, our results might have a more practical value in an era when fake news are becoming prominent,
%as they suggest that these might have different style compared to real news.
%Second, our results provide valuable insights for designing new NLP tasks,\clinic{unclear}
%both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
%We show that these details are actually very significant. 
Second, we establish a new state-of-the-art result on the commonsense story cloze challenge.

\com{
The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
We then present our model, experiments and results in Sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present a further analysis of our results  and a discussion, followed by related work and conclusions.\clinic{Omit this paragraph?}}

\isection{Background: The Story Cloze Task}{ROC_Story}
To understand how different writing tasks affect writing style, 
we focus on the \textit{story cloze task} \cite{Mostafazadeh:2016}. 
While this task was developed to facilitate representation and learning of commonsense story understanding,
its design included a few key choices which  make it ideal for our study. 
We describe the task below.

@@

\paragraph{ROC stories.}

@@

\paragraph{Story cloze task.}
After compiling the story corpus, the {\it story cloze task}---a task based on the corpus---was introduced.
A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
Both endings are required to complete the story using one of the characters in the story context. 
Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.

@@

Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it story cloze task}. 
The task is simple:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
%The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are included in the training set). 
The task was suggested as an extensive evaluation framework:
%as a machine reading task, 
as a commonsense story understanding task, 
as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.

\resolved{\paragraph{A Hard Task.}}\roy{Was a paragraph titled  ``State-of-the-art results". Luke mentioned that this puts the focus on our results rather than on the nature of the task, as we intended, so I merged it into the previous paragraph}
Interestingly, at the time of this submission, 10 months after the
task was first introduced, the published benchmark on this task is
still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
  task website (\url{https://competitions.codalab.org/competitions/15333}) does report higher results (71.1\%), which are still
  unpublished along with the underlying methodology.}
This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad} for which results improved dramatically over a similar or shorter period of time.
This suggests that this task is challenging and that high performance is hard to achieve.
 \resolved{\yc{SQuAD was officially published in Nov 2016. by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper. Given that, the statement of this paragraph seems a bit of overkill...?} \nascomment{it sounds like Yejin is saying that on squad, there was an even faster acceleration?  or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}

In addition, \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
Furthermore, the authors implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
These results indicate that real understanding of text is required in order to solve the task.

\paragraph{Different writing tasks in the story cloze Task.}
Several key design decisions make this task an interesting testbed for the purpose of this paper.\resolved{\clinic{Which purpose?}}
First, the training set for the task (ROC Stories corpus) is not a
training sample in the usual sense,\footnote{I.e., the training
  instances are not drawn from a population similar to the one that future
  testing instances will be drawn from.\roy{I added \textbf{not} here, as otherwise it is confusing}}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
 \resolved{\yc{As far as I understand, this was intentional --- they didn't want
  people to pick up on random superfluous cues that can inevidently
  get into the data creation process, exactly the kind that our work
  picks up. Given that, stating this can be viewed as
  misunderstanding, I'm afraid.} \nascomment{We should maybe say that
  they did this intentionally and concede that our approach goes
  against the intentions of their task design.  But a task that
  insists that systems avoid using features that might encode one kind
of information (like style) is absurd.  Alternately, we could reframe
this not as ``things weren't controlled for'' but instead stick to the
facts here and just describe what they did without judgment.}}

On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets. 
While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
and then asking her to generate a fifth {\it right} ending. 
%This raises the question of whether these different writing setups impose different writing styles. 
% We show that this is indeed the case.

@@

\isection{Surface Analysis of the Story Cloze Task}{Surface}
We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
Our analysis  reveals several style differences between different groups. 
First, {\it original} endings are on average longer (11 words per
sentence) than {\it right} endings (8.75 words), which are in turn
slightly longer than {\it wrong} ones (8.47 words). 
\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings,
which in turn prefer proper nouns, especially compared to {\it original} endings.
\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}

Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings prefer negative ones (``hates''). 
\yc{Again, any cogsci literature on this?} \nascomment{feels
  Pennebaker-ish, that might be a good place to look.}
Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.

@@

        \legend{NN, VBD, PRP, DT, NNP}
    \end{axis}
\end{tikzpicture}
\caption{\label{roc_pos_distribution}POS tags}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
\begin{tikzpicture}
\small
    \begin{axis}[
        width  = 0.4*\textwidth,
        height = 4cm,
      %  major x tick style = transparent,
        ybar=\pgflinewidth,
        x=2.5cm,
       bar width=5pt,
        ymajorgrids = true,
%        ylabel = {Frequency in Corpus (\%)},
        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
        xtick = data,
        scaled y ticks = false,
        %enlarge x limits=0.25,
        ymin=0,
        legend cell align=left,
        legend style={
        		legend columns=-1,
                at={(1,1.05)},
                anchor=south east,
                column sep=1ex
        }
    ]
        \addplot[style={bblue,fill=bblue,mark=none}]
            coordinates {({\it original}, 3) ({\it right}, 3.3) ({\it wrong}, 3.5)};

        \addplot[style={rred,fill=rred,mark=none}]
            coordinates {({\it original}, 2.5) ({\it right}, 1.8) ({\it wrong}, 1.3)};

        \addplot[style={ggreen,fill=ggreen,mark=none}]
            coordinates {({\it original}, 1) ({\it right}, 1.2) ({\it wrong}, 1.4)};

        \addplot[style={brown,fill=brown,mark=none}]
            coordinates {({\it original}, 0) ({\it right}, 0) ({\it wrong}, 0.6)};

        \addplot[style={gray,fill=gray,mark=none}]
            coordinates {({\it original}, 0.9) ({\it right}, 0.2) ({\it wrong}, 0.1)};
